\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-11-25 exps.tex
cont

Table~\ref{fig:comparison} shows the result of our algorithm applied to
each benchmark program. Note that we allowed the compiler to find the
minimum upper real-time bounds for all delay constructs, e.g. bounded
(\texttt{M..N}) or exact (\texttt{M..M}) delays, when it fails to find a
feasible solution. However, a user can prohibit this behavior through
configuration that such case is an error.

>>>>

Table~\ref{fig:comparison} shows the result of our algorithm applied to
each benchmark program. Note that we allowed the compiler to relax the
upper real-time bounds even for bounded (\texttt{M..N}) or exact
(\texttt{M..M}) delays when it fails to find a feasible solution.
However, a user can prohibit this behavior through configuration that
such case is an error.
